\hl{On the use of Generative adversarial neural networks for computing photonic crystal fiber optical properties}

### 2020-03-17 docs/paper/paper.tex
fix: doc

\subsection{Artificial neural network design}
\label{ssec:ann}
The ANN model is a fully-connected feed-forward MLP (Multi Layer Perceptron). Table(num) summarizes the details of the model consisting of an input layer. To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit. To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.

@@

A labelled data-set of only 432 samples was collected in this work, through simulations using FV-FEM. The length of the data-set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent. The data-set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for 3 different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]). Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing. This data was preprocessed before fed in the networks. The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$. Finally, we transform the confinement loss to the log scale.

@@

We train the ANN model for more than 2000 epochs, starting from the original data set. Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection. The following table summarizes the hyper-parameters chosen for the ANN model:
\begin{table}[h]
\centering
\scalebox{1.5}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
\hline
336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
\hline
336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
\hline
    \end{tabular}
}
\caption{Hyper-parameters chosen for the ANN model}
\end{table}

\newpage
The MSE on the training sets ranged from 0.0030 to 0.0050. For all data sets the MSE on the training sets decreased in an acceptable manner. Next, we plot the predictions the ANN model made after training using only the original. As shown in the following figure data-set.

@@

During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in figure(num).
In this sub-section we discuss the results of augmenting the real data set with generated samples. Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data. There are several reasons that is driving our ANN model predictions in the wrong way. Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data. Furthermore, the generated data might lack realism. Or the sampling strategy adopted is poor. But the most convincing reason is the limited original data set size of 336 samples, used to train the WGAN model in the first place. After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to increase the accuracy of the ANN model by artificially expanding the original set.

\hspace{-0.07\textwidth}
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			xlabel=$Epochs$, 
			ylabel=$ Training $ $ MSE $,
			title={Training loss function of the Critic network},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[line width=1pt,solid,color=blue]  %
			table{wgan_tr_loss.txt};
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 1000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_1000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 2000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_2000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 3000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_3000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
\newpage
It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in figure(num).

>>>>

\subsection{Artificial neural network design}
\label{ssec:ann}
The ANN model is a fully-connected feed-forward Multi Layer Perceptron (MLP) model. Table(num) summarizes the details of the model. To reduce over fitting we use the Early stopping method, by saving checkpoints where the best validation mean squared error occurred as we iterate before the model starts to over fit. To accelerate training and mitigate the problem of internal covariate shift Batch Normalization algorithm [14] was used.

@@

A labelled data set of only 432 samples was collected in this work, through simulations using FV-FEM. This length of the data set made the task of building ANN model look quiet impossible, however the results were satisfying to some extent. This data set consists of the wavelength $\lambda$, index of refraction $n_{analyte} $, air-hole to air-hole distance $ \Lambda $, and the air holes radii per ring $d1$, $d2$ and $d3$, taken as our independent variables. The labels are the confinement loss of the PCF. The set consists of nine different configurations of the geometric properties ($ \Lambda $, d1, d2, d3), for each configuration the confinement loss was calculated for three different analytes (Water (n=1.33), Ethanol (n=1.35) and several commercial hydrocarbon mixtures (n=1.36) [35]). Seven configurations were randomly selected for training both the WGAN-GP and the ANN, one configuration was held out for validation, and the last configuration for testing. This data was preprocessed before fed in the networks. The indices of refraction  are very close, which made it quiet difficult for the neural networks to differentiate between them, after many trials, the best choice was to take only the tens digit of ${134, 135, 136}$, giving ${4, 5, 6}$. Finally, we transform the confinement loss to the log scale, for the purpose of shortening the distance between the confinement loss points

@@

We train the ANN model for more than 2000 epochs, starting from the original data set. Then we augment the latter set by 1000 generated samples by our WGAN-GP, which will be demonstrated in the next subsection, and train again with the new augmented data set. The following table summarizes the hyper-parameters chosen for the ANN model:
\begin{table}[h]
\centering
\scalebox{1.5}{
    \begin{tabular}{|l|l|l|l|l|}
    \hline
Length of the training data-set & Learning rate& Mini batch size & $\beta_{1}$ & $\beta_{2}$\\
\hline
336 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 1000 & $ 1\times10^{-04} $ & 8 & 0.9 & 0.999 \\
\hline
336 + 2000 & $ 2\times10^{-04} $ & 16 & 0.9 & 0.999 \\
\hline
336 + 3000 & $ 2.5\times10^{-04} $ & 20  & 0.9 & 0.999 \\
\hline
    \end{tabular}
}
\caption{Hyper-parameters chosen for the ANN model}
\end{table}

\newpage
The MSE on the training sets ranged from 0.0030 to 0.0050. For all training data sets the MSE decreased in an acceptable manner. Next, we plot the predictions the ANN model made after training using only the original. As shown in the following figure data-set.

@@

During training, the metric used to monitor the WGAN-GP is the loss function of the Critic network. Its convergence signals the ending of the training phase, shown in Figure(num).
In this subsection we discuss the results of augmenting the real data set with generated samples. Figure(num) demonstrates the predictions made by the ANN model after training with different sizes of the data set.
This might look paradoxical to what we mentioned earlier, that ANN model benefit from large amounts of data. There are several reasons for why our ANN model is driven in the wrong direction. Even though our WGAN-GP seemed well trained, there still a domain gap between the real data and the generated data, or the expansion of data is growing in the wrong direction to that of entirely containing the real data. Furthermore, the generated data might lack realism. Or the sampling strategy adopted is poor. But the most convincing reason is the limited original training data set size of 336 samples, used to train the WGAN model in the first place. After all, with 1000 generated data samples the ANN model made quiet accurate predictions with which we are satisfied, that is we have achieved what we set out to accomplish at the beginning, to improve the accuracy of the ANN model by artificially expanding the original set.

\hspace{-0.07\textwidth}
\begin{figure}[h]
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			xlabel=$Epochs$, 
			ylabel=$ Training $ $ MSE $,
			title={Training loss function of the Critic network},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[line width=1pt,solid,color=blue]  %
			table{wgan_tr_loss.txt};
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
    \begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 1000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_1000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $, 
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 2000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_2000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}\hspace{0.05\textwidth}
\begin{subfigure}{.5\textwidth}
			\begin{tikzpicture}
			\begin{axis}[
			legend pos=north west,
			xlabel=$Actual $ $ loss $ $ in $ $ Log(db/cm) $,
			ylabel=$Predicted $ $ loss $ $ in $ $ Log(db/cm) $,
			title={Length of the training dataset = 336 + 3000},
			grid=both,
			minor grid style={gray!25},
			major grid style={gray!25},
			width=1.1\linewidth]
			\addplot[
			only marks,
			mark size=2.9pt, mark=o, color=red, fill=red] %
			table{dataset_3000.txt};
			\addlegendentry{$Predicted$}
			\addplot[line width=1pt,solid,color=blue]  %
			table{y.txt};
			\addlegendentry{$Actual$}
			\end{axis}
			\end{tikzpicture}
\end{subfigure}
\caption{}
\end{figure}
\newpage
It can readily be seen that by augmenting with 1000 samples the ANN model made the best predictions, which then can be better viewed when we plot the confinement loss of the PCF versus the wavelength($\lambda$) in Figure(num).
